paper1_results_figs_slimmed_50_rr

### 2016-06-20 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
added specificity calcs, removed mix either from one fig and added gridlines back into PRCC plots

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             ggtitle(paste(strat_name[strategy_num])) +
             xlab(NULL) 
  }

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.8))

@@

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

@@

  #to rearrange order of legend entries
  ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential", "Mix either")) #, labels=c("MBB", "MAA", "MCC"))

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

@@

## Fig. x5 Effectiveness and exposure together determine most of whether resistance arises slower under adaptive mixture or sequential strategies

1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.

@@

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
  #(Intercept)          x1 
  #1.019330    0.560508

@@

Red triangles are those runs in which resistance reached the threshold at the same time in the two strategies (and are repeated in both panels). The red line is a linear model through these same points.

## Fig. x6 Modifying the previous plot to show where resistance arises over 20% slower in an adaptive mixture strategy versus sequential.

1. The line fitted to runs where resistance is reached at the same time for mixture and sequential is retained. Less of the parameter space favours the adaptive mixture under these constraints.

@@

@@

    #find unequal runs
    unequal <- ggSubset[ggSubset$resist_start_lo_div_hi < 0.01,]
    nrow(ggSubset)
    nrow(unequal)
    #2721 out of the 6189 remaining runs

    #in how many runs was seq better than mix
    sum(unequal$seq_better_mix20.5)
    #311

@@

>>>>

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             ggtitle(paste(strat_name[strategy_num])) +
             xlab(NULL) 
  }

  #to put back in some ref gridlines that are removed by cowplot
  #theme_set(theme_gray())
  theme_set(theme_bw())

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.6))

@@

  #remove insecticide1 & 2 strategies
  #ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #20/6/16 try also removing "Mix either" 
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2","Mix either"), ]

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

@@

  #to rearrange order of legend entries
  #ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential", "Mix either")) 
  #20/6/16 try removing "Mix either" 
  ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential"))

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=0.5) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

@@

## Fig. x5 Effectiveness and exposure together determine most of whether resistance arises slower under adaptive mixture or sequential strategies
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.
```{r, eval=TRUE, echo=FALSE, fig.height=6}

@@

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
  #(Intercept)          x1 
  ## 1.0746184 0.5590287

  #20/6/16 calculated T/F positives & negatives, according to the linear model calculation
  #this is a very heath-robinson way of doing, must be a better way
  #so I want to find whether a point is above or below the line (and probably ignore zeros where mix & sequence the same)
  #the eq is approx y=0.56*x+1.07
  #so I could create a new column that has the expected lm val of added effectivenesses
  #where +ve is mix better
  #true+ve : effectiveness1+2 > lm & mixA_minus_seq0.5>0
  #true-ve : effectiveness1+2 < lm & mixA_minus_seq0.5<0
  #false+ve : effectiveness1+2 > lm & mixA_minus_seq0.5<0
  #false-ve : effectiveness1+2 < lm & mixA_minus_seq0.5>0  
  ggSubset$l_mod_eff <- l_mod$coefficients[2] * ggSubset$exposure + l_mod$coefficients[1]

  #BEWARE that this sets 0s (where mix & sequence are equal) to NA
  ggSubset$l_mod_confusion <- 
    ifelse ( (ggSubset$effectiveness_insecticide1+ggSubset$effectiveness_insecticide2) > ggSubset$l_mod_eff,
               ifelse(ggSubset$mixA_minus_seq0.5>0,"TP",ifelse(ggSubset$mixA_minus_seq0.5<0,"FP",NA))

            ,ifelse(ggSubset$mixA_minus_seq0.5<0,"TN",ifelse(ggSubset$mixA_minus_seq0.5>0,"FN",NA))
            )

  table(ggSubset$l_mod_confusion)

  #  FN   FP   TN   TP 
  #602  219 3834 2787

  #sensitivity or true positive rate TPR=TP/(TP+FN)
  TPR = length(which(ggSubset$l_mod_confusion=="TP")) / (length(which(ggSubset$l_mod_confusion=="TP"))+length(which(ggSubset$l_mod_confusion=="FN")))
  #specificity (SPC) or true negative rate SPC=TN/(TN+FP)
  SPC = length(which(ggSubset$l_mod_confusion=="TN")) / (length(which(ggSubset$l_mod_confusion=="TN"))+length(which(ggSubset$l_mod_confusion=="FP")))

  cat("sensitivity(TPR) : ",TPR)#,"\n")
  cat("specificity(SPC) : ",SPC)#,"\n")

@@

```
Red triangles are those runs in which resistance reached the threshold at the same time in the two strategies (and are repeated in both panels). The red line is a linear model through these same points. 
\pagebreak

## Fig. x6 Modifying previous plot to show where resistance arises over 20% slower for adaptive mixture versus sequential.

1. The line fitted to runs where resistance is reached at the same time for mixture and sequential is retained. Less of the parameter space favours the adaptive mixture under these constraints.
```{r, eval=TRUE, echo=FALSE, fig.height=6}

@@

#20/6/16 calculated T/F positives & negatives, according to the linear model calculation
  #this is a very heath-robinson way of doing, must be a better way
  #so I want to find whether a point is above or below the line (and probably ignore zeros where mix & sequence the same)
  #the eq is approx y=0.56*x+1.07
  #so I could create a new column that has the expected lm val of added effectivenesses
  #where +ve is mix better
  #true+ve : effectiveness1+2 > lm & mixA_minus_seq0.5>0
  #true-ve : effectiveness1+2 < lm & mixA_minus_seq0.5<0
  #false+ve : effectiveness1+2 > lm & mixA_minus_seq0.5<0
  #false-ve : effectiveness1+2 < lm & mixA_minus_seq0.5>0  
  ggSubset$l_mod_eff <- l_mod$coefficients[2] * ggSubset$exposure + l_mod$coefficients[1]

  #BEWARE that this sets 0s (where mix & sequence are equal) to NA
  ggSubset$l_mod_confusion <- 
    ifelse ( (ggSubset$effectiveness_insecticide1+ggSubset$effectiveness_insecticide2) > ggSubset$l_mod_eff,
               ifelse(ggSubset$mixA_not20pc_better_seq0.5==0,"TP",ifelse(ggSubset$mixA_not20pc_better_seq0.5==1,"FP",NA))

            ,ifelse(ggSubset$mixA_not20pc_better_seq0.5==1,"TN",ifelse(ggSubset$mixA_not20pc_better_seq0.5==0,"FN",NA))
            )

  table(ggSubset$l_mod_confusion)

  #  FN   FP   TN   TP 
  ## 251 468 6178 915

  #sensitivity or true positive rate TPR=TP/(TP+FN)
  TPR = length(which(ggSubset$l_mod_confusion=="TP")) / (length(which(ggSubset$l_mod_confusion=="TP"))+length(which(ggSubset$l_mod_confusion=="FN")))
  #specificity (SPC) or true negative rate SPC=TN/(TN+FP)
  SPC = length(which(ggSubset$l_mod_confusion=="TN")) / (length(which(ggSubset$l_mod_confusion=="TN"))+length(which(ggSubset$l_mod_confusion=="FP")))

  cat("sensitivity(TPR) : ",TPR)#,"\n")
  cat("specificity(SPC) : ",SPC)#,"\n")

@@

    #find unequal runs
    unequal <- ggSubset[ggSubset$resist_start_lo_div_hi < 0.01,]
    #nrow(ggSubset)
    #nrow(unequal)
    #2721 out of the 6189 remaining runs

    #in how many runs was seq better than mix
    #sum(unequal$seq_better_mix20.5)
    #311

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5} 
#eval=FALSE so this one not displayed
